Programming Language Foundations in Agda

### 2019-07-15 papers/scp/PLFA.tex
fix typo

Section~7 outlines our experience publishing the book as open source
in Github.  We were surprised at how effective this was at eliciting
community participation.  A large number of people have submitted pull
requests to improve the book.

@@

Table~\ref{tab:exams} shows performance on the mock exam and the final
exam for the courses run at Edinburgh and PUC-Rio.  While scores vary
widely on the mock, all students achieve perfection on the
exam.  (The one exception was a PUC-Rio student who did not attend
classes or sit the mock.)  Similar results were achieved at Edinburgh
over the previous five years, using SF as the course textbook and Coq
as the proof assistant.  We consider these results a tribute to the
students' ability to study and learn.

\begin{table}
\begin{center}
  \begin{tabular}{|cc|cc|}
    \hline
    \multicolumn{2}{|c|}{Edinburgh} &
    \multicolumn{2}{c|}{PUC-Rio} \\
    \hline
    Mock & Exam & Mock & Exam \\
    \hline
     15  &  50  &  --  &  40  \\
     29  &  50  &  ~6  &  50  \\
     33  &  50  &  20  &  50  \\
     35  &  50  &  28  &  50  \\
     36  &  50  &  41  &  50  \\
     48  &  50  &  49  &  50  \\
     49  &  50  &  50  &  50  \\
     50  &  50  &  50  &  50  \\
     50  &  50  &  50  &  50  \\
     50  &  50  &  50  &  50  \\
    \hline
  \end{tabular}
\end{center}
\caption{Exam marks}
\label{tab:exam}
\end{table}

@@

The book is published as open-source on Github, under a
Creative Commons CC-BY license.  As the book is an executable
Agda script, it was considered essential that anyone could
download and execute it.

One sign of a successful publication is that it will attract a few
letters from readers who have noticed typos or other problems.  An
unexpected benefit of publishing on Github is that to date forty
readers have sent pull requests.  Most of these fix typos, but a fair
number make more substantial improvements.  Wen wrote a script that
automatically adds the name of any contributor of an accepted pull
request to the list of acknowledgements, sorted by the number of
accepted requests.  Arguably, a different metric, such as total
number of affected lines, might be more appropriate.

>>>>

Section~7 outlines our experience publishing the book as open source
in GitHub.  We were surprised at how effective this was at eliciting
community participation.  A large number of people have submitted pull
requests to improve the book.

@@

For the courses run at Edinburgh and PUC-Rio, the scores vary
widely on the mock, but all students achieve perfection on the
exam.  (The one exception was a PUC-Rio student who did not attend
classes or sit the mock.)  Similar results were achieved at Edinburgh
over the previous five years, using SF as the course textbook and Coq
as the proof assistant.  We consider these results a tribute to the
students' ability to study and learn.

\section{Software}

The book is written using a combination of literate Agda and Markdown.  At the
time of writing, the book is published using GitHub Pages and the Jekyll static
site generator.  The book is open source---the source is currently also hosted
on GitHub, under a Creative Commons CC-BY license.  The open-source aspect is
important---as the book is written in literate Agda, it is essential that anyone
can download and execute the source.

We maintain a number of tools, which play various roles in rendering the book in
all its ``glorious clickable HTML''. We render the literate Agda to highlighted
HTML using Agda's HTML backend. In addition to highlighting, this inserts
clickable links, linking each constructor and function to the site of its
definition.  However, the links Agda inserts are local and don't match the
structure of the book.  We maintain a script, \texttt{highlight.sh}, which fixes
these links, rerouting links to the standard library to the online version, and
correcting links to local modules.

(Before the release of Agda 2.6, Agda did not support highlighting embedded
literate code using HTML.  To address this, we wrote \texttt{agda2html}, a tool
which rewrote the output of Agda's HTML highlighter to accomplish this. This
tool had much more functionality, including the fixing of links as outlined
above, the stripping of implicit arguments to achieve a Haskell-like look, and
the support for new Markdown constructs for linking to Agda names. However,
Agda 2.6 has incorporated almost all of this functionality.)

The book is built, tested, and published after each commit, using Travis CI, a
web service for continuous integration.  The means that the book is constantly
changing.  To accommodate those who want a more stable version, e.g., for
teaching, we maintain a stable version of the book at
\begin{center}
  \url{http://plfa.inf.ed.ac.uk/stable}
\end{center}
The stable version of the book is only updated much less frequently, and updates
are announced.

We maintain a tool called, simply, \texttt{acknowledgements}, which uses
the GitHub API to automatically extract a list of contributors to the book, and
add them to the Acknowledgements page, each time the book is published.  We
consider anyone who has sent a successful pull requests a contributor, and sort
contributors in the acknowledgments by the number of accepted requests.
Arguably, a different metric, such as total number of affected lines, might be
more appropriate, though any solution may have its flaws.

@@

One sign of a successful publication is that it will attract a few letters from
readers who have noticed typos or other problems.  An unexpected benefit of
publishing on GitHub is that to date forty-one readers have sent a total of
\emph{two hundred seventy-five} pull requests.  Most of these fix typos, but a
fair number make more substantial improvements.
